What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-20 manuscript.Rmd
Addressing R1, comments 11 and 12

Note also that while ROIs the size of quadrants are feasible, good calibration is important. Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.

There are a number of other interventions that might increase precision and should be investigated. For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise. It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback. These and other options should be investigated in order to determine how much they might improve precision.

>>>>

Note also that while ROIs the size of quadrants are feasible, good calibration is important. Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 50% validation accuracy. While stricter thresholds may decrease noise, they come at a cost. In preliminary analysis, we found that a threshold of 75% somewhat increased effect size in Exp. 4, but at the cost of reducing the sample size from 35 to 19. However, it could be helpful to more systematically investigate the optimal threshold and whether this varies by size of ROI.

There are a number of other interventions that might increase precision and should be investigated. For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise. It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback. Similarly, it may be profitable to systematically study the parameters of eyegaze validation, for instance the number of validation points and the maximum distance allowed between gaze and target (set to 200px in the present study). These and other options should be investigated in order to determine how much they might improve precision.
